### 2020-12-13 exploratory/2020-11_Nov-Dec/plots.Rmd
Use boxplots instead of jitters for fit-db

```{r mcc_fit-db}
optifit_dbs %>% 
  ggplot(aes(x=method, y=mcc, color=ref)) +
  geom_hline(aes(yintercept = mean_mcc), sum_opticlust) +
  geom_jitter(alpha = 0.5) + 
  facet_wrap('dataset') +
  ylim(0, 1) +
  labs(title='OTU Quality: OptiFit with reference databases',
       caption='Black line: _de novo_ clustering') +
  theme(plot.caption = element_markdown())
```

```{r fraction-mapped_fit-db}
optifit_dbs %>% #filter(method == 'closed') %>% 
  ggplot(aes(x=dataset, y=fraction_mapped, color=ref)) +
  geom_jitter(alpha = 0.5) + 
  facet_wrap('method') +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit") +
  theme(plot.caption = element_markdown())
```

@@

```{r mcc_vsearch}
vsearch_join 
  ggplot(aes(x = method, y = mcc, color = tool)) +
  geom_boxplot() +
  facet_wrap('dataset') +
  ylim(0, 1) + 
  labs(x = '')
```

```{r sec_vsearch}
vsearch_join 
  ggplot(aes(x = method, y = sec, color = tool)) +
  geom_boxplot() +
  facet_wrap('dataset') +
  labs(x = '')
```

```{r diversity_vsearch}
vsearch_join 
  ggplot(aes(x = method, y = shannon, color = tool)) +
  geom_boxplot() +
  facet_wrap('dataset') +
  labs(x = '')
```

```{r fraction-mapped_vsearch}
vsearch_join #filter(method == 'closed') %>% 
  ggplot(aes(x = dataset, y = fraction_mapped, color = tool)) +
  geom_boxplot() + 
  ylim(0, 1) +
  facet_wrap('method') +
  labs(title="Sequences mapped during closed-reference OptiFit") +
  theme(plot.caption = element_markdown())
```

@@

```{r metrics_all-human}
all_human %>% 
  pivot_longer(c(mcc, sec, mem_gb, fraction_mapped), names_to = 'metric') %>% 
  ggplot(aes(strategy, value, color = tool)) +
  geom_boxplot() +
  facet_wrap('metric', scales = 'free') +
  labs(x='', y='', 
       title="mothur vs. vsearch", 
       caption = 'The human dataset is shown here. The patterns are similar with other datasets.')
```

>>>>

```{r mcc_fit-db}
optifit_dbs %>% 
  ggplot(aes(x=method, y=mcc, color=ref)) +
  geom_hline(aes(yintercept = mean_mcc), sum_opticlust) +
  geom_boxplot() + 
  facet_wrap('dataset') +
  scale_color_manual(values=tri_colors) +
  ylim(0, 1) +
  labs(title='OTU Quality: OptiFit with reference databases',
       caption='Black line: _de novo_ clustering') +
  theme(plot.caption = element_markdown())
```

```{r fraction-mapped_fit-db}
optifit_dbs %>% filter(method == 'closed') %>% 
  ggplot(aes(x=dataset, y=fraction_mapped, color=ref)) +
  geom_boxplot() + 
  facet_wrap('method') +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit") +
  theme(plot.caption = element_markdown())
```

@@

```{r mcc_vsearch}
vsearch_join %>% 
  ggplot(aes(x = method, y = mcc, color = tool)) +
  geom_boxplot() +
  facet_wrap('dataset') +
  ylim(0, 1) + 
  labs(x = '')
```

```{r sec_vsearch}
vsearch_join %>% 
  ggplot(aes(x = method, y = sec, color = tool)) +
  geom_boxplot() +
  facet_wrap('dataset') +
  labs(x = '')
```

```{r diversity_vsearch}
vsearch_join %>% 
  ggplot(aes(x = method, y = shannon, color = tool)) +
  geom_boxplot() +
  facet_wrap('dataset') +
  labs(x = '')
```

```{r fraction-mapped_vsearch}
vsearch_join %>% #filter(method == 'closed') %>% 
  ggplot(aes(x = dataset, y = fraction_mapped, color = tool)) +
  geom_boxplot() + 
  ylim(0, 1) +
  facet_wrap('method') +
  labs(title="Sequences mapped during closed-reference OptiFit") +
  theme(plot.caption = element_markdown())
```

@@

```{r metrics_all-human}
all_human %>% 
  pivot_longer(c(mcc, sec, mem_gb, fraction_mapped), names_to = 'metric') %>% 
  ggplot(aes(strategy, value, color = tool)) +
  geom_boxplot() +
  facet_wrap('metric', scales = 'free') +
  labs(x='', y='',  
       caption = 'Only the human dataset is shown here. The patterns are similar with other datasets.')
```
